ForOpenCL: Transformations Exploiting Array Syntax in Fortran for Accelerator Programming

### 2011-06-27 papers/GPUScA-2011/performance.tex
performance table

Several timing measurements were made by varying the size of the array state
variables.  An average time was obtained by executing 100 iterations of the outer
time-advance loop that called the OpenCL kernel. This tight loop kept the OpenCL
kernel supplied with threads to take advantage of potential latency hiding by
the NVIDIA GPU.  Any serial code within this loop (not present in this study)
would have reduced the measured values.

>>>>

Several timing measurements were made by varying the size of the array state
variables.  The performance measurements are shown in Table~\ref{table:performance}.  An average time was obtained by executing 100 iterations of the outer
time-advance loop that called the OpenCL kernel. This tight loop kept the OpenCL
kernel supplied with threads to take advantage of potential latency hiding by
the NVIDIA GPU.  Any serial code within this loop (not present in this study)
would have reduced the measured values.

\begin{table}
\begin{center}
	\begin{tabular}{|c|c|c|c|}
	\hline Array width & F90 & GPU (16x8) & Speedup \\ \hline\hline
	16   & 0.025 ms & 0.017 ms & 1.5  \\ \hline
	32   & 0.086    & 0.02     & 4.3  \\ \hline
	64   & 0.20     & 0.02     & 10.0 \\ \hline
	128  & 0.76     & 0.036    & 21.1 \\ \hline
	256  & 3.02     & 0.092    & 32.8 \\ \hline
	512  & 12.1     & 0.32     & 37.8 \\ \hline
	1024 & 49.5     & 1.22     & 40.6 \\ \hline
	1280 & 77.7     & 1.89     & 41.1 \\ \hline
	2048 & 199.1    &  4.82    & 41.3 \\ \hline
	4096 & 794.7    & 19.29    & 41.2 \\ \hline
	\end{tabular}
\end{center}
\caption{Performance measurements for the shallow-water code.  All times reported in milliseconds.}
\label{table:performance}
\end{table}
